Radio Emission from Red-Giant Hot Jupiters

### 2015-11-12 reply2referee.txt

## Fig 3: the numbers on the RHS have no units...they are probably
## fluxes, but they should be shown.

  We appreciate this feedback. We have indicated the unit in the title
  of Figure 3.

## Section 4:
## 
## Much of this section could be cut, saving perhaps section
## 4.2. Predictions for observations with different facilities have been
## made many times before.

  We would like to retain Section 4.1; indeed, when we talked about
  this work with people, they often ask me about it.  We are unaware
  of any predictions in the literature that make it easy for the
  reader to estimate the required duration of the observations
  describe in our manuscript.  We also think Section 4.3 and 4.4 are
  useful.  To our knowledge, we know of no such comparison for state of
  the art facilities that is up to date for late 2015, nor do we know
  of any consolidation of this information in one publication.
  Predictions for future facilities become rapidly out of date as
  projects are descoped (or "rebaselined" in the case of the SKA), and
  many sensitivity predictions for existing instruments were made
  before the instrument was built.  Including the latest measured 
  performance or design specifications is crucial to assess observing 
  feasibility.
  In section 4.4, we discuss the important point that one can exploit 
  the unique time variability of these signatures for detection.  
  We think this is a crucial point to consider, as direct imaging 
  would be impossible in the face of confusion from both Galactic and
  extragalactic sources (which are brighter but will not vary on the same
  time scale).

### 2015-11-12 ms.tex
argument about the expected number of detection, in response to referee's last comment

Figure \ref{fig:observability} displays the estimated radio flux from Jupiters [A] and [B] around M-type red giants within 300~pc. 
Jupiters are placed at 1 AU and at 5 AU for reference. 
The difference of the symbols indicates whether the radio emission can escape from the system (circle), i.e., $\nu _{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$,  or not (cross). 
Assuming Jupiter-mass planets which typically have the maximum cyclotron frequency at $10-100$~MHz depending on the age, a reasonable number of systems have potential to emit radio wave at the level above $\sim 10~\mu {\rm Jy}$  out to $\sim 100-300$ pc, while those with the highest mass-loss rate would suffer from the plasma cut-off of the stellar wind. 
For more massive planets with the maximum cyclotron frequency at around $100-1000$~MHz, the radio flux is lowered due to its dependence on $B^{-1/3}$ (equation (\ref{eq:F_nu})), but more likely to get to the Earth. $10~M_{\rm J}$ planets at $\sim 1$ AU may be detectable out to $\sim 200$~pc.

>>>>

Figure \ref{fig:observability} displays the estimated radio flux from Jupiters [A] and [B] around M-type red giants within 300~pc. 
Jupiters are placed at 1 AU and at 5 AU for reference. 
The difference of the symbols indicates whether the radio emission can escape from the system (circle), i.e., $\nu _{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$,  or not (cross). 
Assuming Jupiter-mass planets \revise{}{at 1 AU (5 AU)} which typically have the maximum cyclotron frequency at $10-100$~MHz depending on the age, \revise{a reasonable number of}{148 (44)} systems have potential to emit radio wave at the level above $\sim 10~\mu {\rm Jy}$  out to $\sim 100-300$ pc, while those with the highest mass-loss rate would suffer from the plasma cut-off of the stellar wind. 
For more massive planets with the maximum cyclotron frequency at around $100-1000$~MHz, the radio flux is lowered due to its dependence on $B^{-1/3}$ (equation (\ref{eq:F_nu})), but more likely to get to the Earth. $10~M_{\rm J}$ planets at $\sim 1$ AU may be detectable out to $\sim 200$~pc.

\revise{}{Let us also consider the expected number of radio detection from RGHJs taking account of the occurrence rate of Jovian planets. %
Observations suggest that the occurrence rate of planets with masses $M_{\rm J} < M_p \sin i < 15 M_{\rm J}$ in orbits $1 {\rm AU} < a < 5 {\rm AU}$ around F, G, or K stars is $\sim $ 3.5\% \citep{cumming2008}.  %
Therefore, given that 148 (44) systems with 1$M_{\rm J}$ planets at 1 AU (5 AU) have potential to emit $>10 \mu {\rm Jy}$, about 2-5 would actually be emitting the radio wave of our interest. %
For larger planets ($M_p>2M_{\rm J}$), the number of potentially detectable systems are less, due to the $B^{-1/3}$ dependence of the spectral flux: the number of systems where a 10 $M_{\rm J}$ planet at 1 AU (5 AU) emit $>10\mu {\rm Jy}$ is 21 (5). Since the occurrence rate of such larger planets in the same orbital region is $\sim 3.1\%$ \citep{cumming2008}, one could expect additional $\sim 1$ radio source detection from larger planets with sensitivity 10$\mu {\rm Jy}$. %
}
